---
title: "p8105_hw5_yx2638"
author: "Yifei Xu"
date: "2022-11-10"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(janitor)
library(readr)
library(rvest)
```


### Problem 2

First, we read the data from the GitHub repository. 
```{r, message=FALSE}
data_url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicide = read_csv(url(data_url)) 
```
The raw dataset collects data on homicides in 50 large U.S. cities. It has `r nrow(homicide)` observations of homicides and `r ncol(homicide)` key variables represent uid, reported date, victims' last name, first name, race, age, sex, city, state, latitude, longitude, and disposition.


Next, we create a city_state variable and a resolution variable to indicate whether the homicides were solved.
```{r}
homicide_tidy = homicide %>%
  mutate(city_state = str_c(city, state, sep = ", "),
         resolution = case_when(disposition == "Closed by arrest" ~ "solved",
                                disposition == "Closed without arrest" ~ "unsolved",
                                disposition == "Open/No arrest" ~ "unsolved")) %>% 
  select(city_state, everything()) 
  
```

Then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.
```{r}
# total number of homicides
homicide_tidy %>%
  group_by(city_state) %>%
  summarise(num_homicides = n())

# number of unsolved homicides
homicide_tidy %>%
  filter(resolution == "unsolved") %>%
  group_by(city_state) %>%
  summarise(num_unsolved_homicides = n())

```








