---
title: "p8105_hw5_yx2638"
author: "Yifei Xu"
date: "2022-11-10"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(janitor)
library(readr)
library(rvest)
```


### Problem 2

First, we read the data from the GitHub repository. 
```{r, message=FALSE}
data_url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicide = read_csv(url(data_url)) 
```
The raw dataset collects data on homicides in 50 large U.S. cities. It has `r nrow(homicide)` observations of homicides and `r ncol(homicide)` key variables represent uid, reported date, victims' last name, first name, race, age, sex, city, state, latitude, longitude, and disposition.


Next, we create a city_state variable and a resolved variable to indicate whether the homicides were solved.
```{r}
homicide_tidy = homicide %>%
  mutate(city_state = str_c(city, state, sep = ", "),
         resolved= case_when(disposition == "Closed by arrest" ~ "solved",
                                disposition == "Closed without arrest" ~ "unsolved",
                                disposition == "Open/No arrest" ~ "unsolved")) %>% 
  select(city_state, everything()) 
  
```

Then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.
```{r}
city_summary = homicide_tidy %>%
  group_by(city_state) %>%
  summarise(num_homicides = n(),
            num_unsolved_homicides = sum(resolved == "unsolved")) 

city_summary %>% knitr::kable(col.names = c("City", "Total number of homicides", "Number of unsolved homicides"),
               caption = "Homicide Summary Within Cities")
```

Below is the estimation of the proportion of homicides that are unsolved in Baltimore, MD.
```{r}
bal_homicide = homicide_tidy %>%
  filter(city_state == "Baltimore, MD")

bal_summary = bal_homicide %>%
  group_by(city_state) %>%
  summarise(num_homicides = n(),
            num_unsolved_homicides = sum(resolved == "unsolved"),
            prop_unsolved_homicides = num_unsolved_homicides/num_homicides) 

bal_test = prop.test(x = bal_summary %>% pull(num_unsolved_homicides),
                     n = bal_summary %>% pull(num_homicides))

est_prop = bal_test %>% broom::tidy() %>%
  pull(estimate) %>%
  round(digit = 3)

conf_low = bal_test %>% broom::tidy() %>%
  pull(conf.low) %>%
  round(digit = 3)

conf_high = bal_test %>% broom::tidy() %>%
  pull(conf.high) %>%
  round(digit = 3)

```

The estimate proportion of unsolved homicides in Baltimore, MD is `r est_prop` and the confidence interval is `r paste("[", conf_low, ", ", conf_high, "]", sep ="")`.


We will run proportion test for each of the cities in the dataset.
```{r, message=FALSE}
results_df = 
  city_summary %>% 
  mutate(prop_test = map2(.x = num_unsolved_homicides, .y = num_homicides, ~prop.test(x = .x, n = .y)),
         tidy_test = map(.x = prop_test, ~broom::tidy(.x))) %>% 
  select(-prop_test) %>% 
  unnest(tidy_test) %>% 
  select(city_state, estimate, conf.low, conf.high)
```





